Text embedding models yield high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-02-01 paper/main.tex
addressed (some of) ACH's comments

>>>>

A common approach to assessing students' learning is to compile a set of quiz
questions, tally up the proportion of correctly answered questions, and provide
the student with feedback in the form of a letter grade. Although a numerical
or letter grades give \textit{some} indication about whether the student has
mastered the to-be-learned material, any single measure of performance on a
complex task is at risk of conflating underlying factors, losing relevant
information, and so on. For example, consider the relative utility of the
imaginary map described above that characterizes in detail a student's
knowledge, versus a single annotation saying that the student answered 85\% of
their quiz questions correctly, or that they received a `B'. Here, we show that
the same quiz data required to compute proportion correct scores or letter
grades can be used to instead obtain much more detailed insights into what the
student knows at the time they took the quiz.
